Delta Smelt Enclosure Study 2019 Hybrid Paper Diet Analysis

### 2022-11-18 smelt_2019_allseasons/Zoop 2019.Rmd
few more figure edits

zoop[zoop$Location %in% c("STTD", "STTD-YOLO", "YOLO"),]$Location <- "Yolo"

@@

ggsave("smelt_2019_allseasons/figures/allzoop.png", dpi=250, height=6, width=10, units="in")

@@

ggplot() +
  geom_bar(position = "fill", stat = "identity", data=macro, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Relative Abundance of Macrozoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))

ggsave("smelt_2019_allseasons/figures/macrozoop.png", dpi=250, height=6, width=10, units="in")
```

@@

#order locations
caught.sea$Location <- factor(caught.sea$Location, levels=c("DWSC", "RV", "Yolo", "SM"))

>>>>

zoop[zoop$Location %in% c("STTD", "STTD-YOLO", "YOLO"),]$Location <- "YB"
tow2[tow2$Location %in% c("Yolo"),]$Location <- "YB"

@@

@@

ggplot() +
  geom_bar(position = "fill", stat = "identity", data=macro, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Relative Abundance of Macrozoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))
```

@@

#order locations
caught.sea$Location <- factor(caught.sea$Location, levels=c("DWSC", "RV", "YB", "SM"))
